Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-17 tex/paper1/paper1.tex
updated 171 qs plot

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean fits
  for model $M_{1}$ and $M_{2}$ (blue and red lines respectively; see
  Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
  detail).  The AIC and BIC describing the preference for model over
  the other is also indicated in each plot.  The two components to
  Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the
  location of the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is
  indicated by the green dotted line.  Model fit parameter values and
  their 68\% credible intervals are quoted in Table
  \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

The two models are assessed for how well they describe the data in two
different ways.

Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that model 2 loses less information compared to model 1,
leading to a preference for model 2 over model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).

The AIC reveals which out of a set of models is preferred.  It does
not give an assessment of the goodness-of-fit of each model.
Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is calculated for both models.

>>>>

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean fits
  for model $M_{1}$ and $M_{2}$ (blue and red lines respectively; see
  Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
  detail).  The AIC describing the preference for model over the other
  is also indicated in each plot.  The reduced $chi^{2}_{r}$ statistic
  for Model 1 and Model 2 are given. The two components to Model 2,
  $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the location of
  the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the
  green dotted line.  Model fit parameter values and their 68\%
  credible intervals are quoted in Table \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

{\bf The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}

{\bf The AIC reveals which out of a set of models is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is
  calculated for both models.}
